---
title: "Dummy example on cracking the stock market" 
format: gfm
---

```{r}
library(tidyverse)
```


So... What if we were to randomly sample *k* companies out of the S&P 500 list?
Is it possible that we could beat the average revenue of the whole market? (**Yes...**)
And what if we would pick another subset (be it *k* as in number of companies or *p* - portion of the market)?

And if we pick a new subset, why dont we just pick MANY subsets?
Well,
If we were to pick ALL possible subsets, the average revenue would be the same as the average revenue of the whole market. This is a simple soncept in statistics that states that the average of the sampling distribution of the mean is equal to the population mean (Expected value).

But stats tend to be borring... Let's look at a dummy example and keep an eye on the average as we go through this.

#### First, Let's pick a few companies to play with!
```{r}
company = c('google','microsoft','twitter','facebook','instagram','youtube','apple')
```

#### Now, let's simulate the stock prices for 8 days (day 0 and 7 more)
```{r}
set.seed(12)
sp7 <- 
  tibble(
  day = rep(0:7,length(company)),
  companies = rep(company,each=8),
  start_value = round(rnorm(length(company)*8,100,5),1),
  revenue = round(runif(length(company)*8,-3,3),1)
) |> 
  mutate(
    end_value = start_value + revenue,
    start_value = lag(end_value, default = first(start_value)),
    .by = companies)
```
```{r}
sp7
```

### The average revenue across all companies is 0.318
```{r}
round(mean(sp7$revenue),3)
```

### Average revenue for each company 
```{r}
sp7 |> summarise(revenue = mean(revenue), .by = companies) |> 
```
##### obviously, this average is also 0.18
```{r}
sp7 |> summarise(revenue = mean(revenue), .by = companies) |> 
  summarise(revenue = mean(revenue))
```

### but what if we would pick two companies and go only with them throught time? could we beat the average?

```{r}
random_camponies <- sample(company,2)
```
#### attempt 1

```{r}
paste0('Average revenue for ', paste(random_camponies,collapse = ' & '),':') 
sp7 |> filter(companies %in% random_camponies) |> 
  summarise(roi = mean(revenue), .by = companies) |> 
  print()|> 
  summarise(revenue = mean(roi))
```
and attempt 2
```{r}
paste0('Average revenue for ', paste(random_camponies,collapse = ' & '),':') 
sp7 |> filter(companies %in% random_camponies) |> 
  summarise(roi = mean(revenue), .by = companies) |> 
  print()|> 
  summarise(revenue = mean(roi))

```
and 3?
```{r}
paste0('Average revenue for ', paste(random_camponies,collapse = ' & '),':') 
sp7 |> filter(companies %in% random_camponies) |> 
  summarise(roi = mean(revenue), .by = companies) |> 
  print()|> 
  summarise(revenue = mean(roi))
```
Ok... Let's try all possible combinations of a subset of 2 companies. KEEP THINGS SIMPLE!!!

```{r}
combinations <- combn(company,2) |> t() |> as_tibble() |> 
  set_names(c('company1','company2'))
```

Calculate the average revenue for each combination
```{r}
get_revenue <- function(c1,c2){
  sp7 |> filter(companies %in% c(c1,c2)) |> 
    summarise(roi = mean(revenue), .by = companies) |> 
    summarise(revenue = mean(roi)) |> 
    pull()  
}

```

```{r}
combinations <- mutate(combinations, revenue = map2_dbl(company1,company2,get_revenue))
x <- combinations |> pivot_longer(-revenue,names_to = 'pairs',values_to = 'company') |> 
  mutate(revenue_company=mean(revenue),.by = company) |> 
  mutate(is_better_than_avg = revenue_company > mean(sp7$revenue)) |> 
  select(company, revenue_company,is_better_than_avg) |> distinct()
x
```
And of course, since we picked the entire space of possible combinations,
the mean of all possible combinations is the exact same population mean.
```{r}
 x |> print() |> 
  summarise(revenue = mean(revenue_company))
```

### What does it tell us?
I have no idea... but it was fun to play with this dummy example. 
Choosing things randomly might yield cool or interesting results, but we should always remember that coincidence may occur, and it is up to us to understand the underlying reasons for the results we get. 
It might be that someone was lucky. but then the other person might not be as lucky,
and if all people were to just randomly select 10% of the S&P 500 companies, the average revenue would be the same as the average revenue of the whole market. 



